Analysis 03 - Phase 2 Data

### 2021-11-14 code/analysis_code/01-ALLData.Rmd
Adjust and re-knit analysis script. Re-do modeling still working on it

```{r}
mysummary <- summary(ALL)
```

```{r}
#re-shape of a data frame (for easier saving/showing in manuscript)
summary_df <- data.frame(do.call(cbind, lapply(ALL, summary)))
```
```{r}

```{r}
#save data frame table to file for later use in manuscript
summarytable_file <- here::here("products","Project_Parts","Part_3", "All.Summary.Table.rds")
saveRDS(summary_df, file = summarytable_file)
```

@@

```
######################################
#Data fitting/statistical analysis
######################################
```{r}
# fit glm.
# Ct~X= odds of Ct as response variable
ALL.glm.fit<-glm(Ct~Dilution+Detector+Method, data=ALL)
#look at fit
print(tidy(ALL.glm.fit))

step(ALL.glm.fit, test="LRT")
```
```{r}
# save fit results table  
table_file = here("results", "resulttable.rds")
saveRDS(lmtable, file = table_file)

>>>>

```{r}
mysummary <- summary(ALL)
print(mysummary)
```

```{r eval=FALSE, include=FALSE}
#re-shape of a data frame (for easier saving/showing in manuscript)
summary_df <- data.frame(do.call(cbind, lapply(ALL, summary)))
```
```{r}
All.Summarize<-ALL%>%
  filter(Method!="PCR", Dilution!="NA")%>%
  group_by(Detector, Method, Dilution, Input)%>%
  summarise(n=n(),
            "Average Ct"= mean(Ct)
            )
```

```{r}
#save data frame table to file for later use in manuscript
summarytable_file <- here::here("products","supplement", "All.Summary.Table.rds")
saveRDS(All.Summarize, file = summarytable_file)
```

@@

```
######################################
#Data fitting/statistical analysis
######################################
```{r eval=FALSE, include=FALSE}
# fit glm.
# Ct~X= odds of Ct as response variable
ALL.glm.fit<-glm(Ct~Dilution+Detector+Method, data=ALL)
#look at fit
print(tidy(ALL.glm.fit))

step(ALL.glm.fit, test="LRT")
```
```{r eval=FALSE, include=FALSE}
# save fit results table  
table_file = here("results", "AllGLM.resulttable.rds")
saveRDS(ALL.glm.fit, file = table_file)

### 2021-11-14 code/analysis_code/02-P1.Data.rmd
Adjust and re-knit analysis script. Re-do modeling still working on it

```{r}
#save data frame table to file for later use in manuscript
summarytable_file <- here::here("products","Project_Parts","Part_3", "P1.Summary.Table.rds")
saveRDS(P1summary_df, file = summarytable_file)
```

@@

```{r ALL Data fit and stat analysis}

```
######################################
#Data fitting/statistical analysis
######################################
```{r}
# fit glm.
# Ct~X= odds of Ct as response variable
P1.glm.fit<-glm(Ct~Dilution+Detector+Method, data=P1)
#look at fit
print(tidy(P1.glm.fit))

step(P1.glm.fit, test="LRT")
```
```{r}
# save fit results table  
table_file = here("results", "resulttable.rds")
saveRDS(lmtable, file = table_file)

>>>>

```{r}
#save data frame table to file for later use in manuscript
summarytable_file <- here::here("products","supplement", "P1.Summary.Table.rds")
saveRDS(P1summary_df, file = summarytable_file)
```

@@

### 2021-11-14 code/analysis_code/03-P2.Data.rmd
Adjust and re-knit analysis script. Re-do modeling still working on it

```{r}
p2mysummary <- summary(P2)
```

```{r}
#re-shape of a data frame (for easier saving/showing in manuscript)
P2summary_df <- data.frame(do.call(cbind, lapply(P2, summary)))
```
```{r}

```

```{r}
#save data frame table to file for later use in manuscript
summarytable_file <- here::here("products","Project_Parts","Part_3", "P2.Summary.Table.rds")
saveRDS(P2summary_df, file = summarytable_file)
```

@@

```{r}
P2P1<-P2 %>% 
  filter(Method!="PCR", Tool=="SD"|Tool=="NEG.CTRL")%>%
  ggplot(aes(x=Dilution, y=Ct)) + 
  geom_jitter(aes(color=Method)) + 
  #we also add a linear regression line to it
  geom_smooth(method='glm',alpha=0.2, aes(fill=Method, color=Method))+
  facet_grid(Detector~.)+
  scale_y_reverse()+
  geom_hline(yintercept=27, linetype="longdash", color = "orange")+ #CDC confirmed threshold
  geom_hline(yintercept=37, linetype="longdash", color = "blue")+ #General confirmed threshold
  labs(title="Serial Dilution Comparisons within Phase 2 data")

print(P2P1)
```
```{r}
#save figure
figure_file = here("results","P2-SD-Plot.png")
ggsave(filename = figure_file, plot=P2P1) 
```

```{r ALL Data fit and stat analysis}

```
######################################
#Data fitting/statistical analysis
######################################
```{r}
# fit glm.
# Ct~X= odds of Ct as response variable
P2.glm.fit<-glm(Ct~Dilution+Detector, data=P2P1)
#look at fit
print(tidy(P2.glm.fit))

step(P2.glm.fit, test="LRT")
```

>>>>

```{r}
p2mysummary <- summary(P2)

print(p2mysummary)
```

```{r}
#re-shape of a data frame (for easier saving/showing in manuscript)
P2summary_df <- data.frame(do.call(cbind, lapply(P2, summary)))

print(P2summary_df)
```
```{r}
P2summary_df<-P2%>%
  filter(Dilution!="NA", Tool!="SD", Tool!="*.CTRL")%>%
  mutate(
    Ct.Cat = ifelse(Ct >=38,"Detected","Positive"),
    Ct.Cat=factor(Ct.Cat))%>%
  group_by(Dilution,Method,Ct.Cat)%>%
  summarise(n=n(),
            mean=mean(Ct))%>%
  arrange(Dilution,mean)
```

```{r}
#save data frame table to file for later use in manuscript
summarytable_file <- here::here("products","supplement","P2.Summary.Table.rds")
saveRDS(P2summary_df, file = summarytable_file)
```

```{r Table Best Ct comparing spike and surface recovery}
#Summary of Tool A compared to -1 Serial Dilution Recovery
P2.1Dilution.Summary<-P2%>%
  filter(Dilution=="-1")%>%
  mutate(
    Ct.Cat = ifelse(Ct >=38,"Detected","Positive"),
    Ct.Cat=factor(Ct.Cat))%>%
  group_by(Tool,Method,Ct.Cat)%>%
  summarise(n=n(),
            mean=mean(Ct))%>%
  arrange(mean)%>%
  na.omit(C.Cat)
```
```{r}
#save data frame table to file for later use in manuscript
summarytable_file <- here::here("products","supplement", "P2.-1Dilution.Table.rds")
saveRDS(P2.1Dilution.Summary, file = summarytable_file)
```
A difference of 2 Ct values when compared by methods for each tool type. CDC was better when directly extracted. NTP performed better during a spiked tool and surface recovery procedures. 
Ct loss between Spike and SS recovery are about 3 Ct values, equivalent to a log loss of copies.

@@

```{r warning=FALSE}
P2P1<-P2 %>% 
  filter(Method!="PCR", Tool=="SD"|Tool=="NEG.CTRL")%>%
  ggplot(aes(x=Dilution, y=Ct)) + 
  geom_jitter(aes(color=Method)) + 
  #we also add a linear regression line to it
  geom_smooth(method='glm',alpha=0.2, aes(fill=Method, color=Method))+
  facet_grid(Detector~.)+
  scale_y_reverse()+
  geom_hline(yintercept=27, linetype="longdash", color = "orange")+ #CDC confirmed threshold
  geom_hline(yintercept=37, linetype="longdash", color = "blue")+ #General confirmed threshold
  labs(title="Serial Dilution Comparisons within Phase 2 data")

print(P2P1)
```
```{r warning=FALSE}
#save figure
figure_file = here("results","P2-SD-Plot.png")
ggsave(filename = figure_file, plot=P2P1) 
```
